Illusory Finger Stretching and Somatosensory Responses

### 2025-03-19 manuscript.qmd
Added latex
Switch to stable rocker build

# if (!is_tinytex()){install_tinytex()}

@@

#make eegdata dataframes
eegdata <- data.frame(as.matrix(eegdata))
eegdata_exp <- data.frame(as.matrix(eegdata_exp))
colnames(eegdata) <- c('V1','V2','V3','V4')
colnames(eegdata_exp) <- c('V1','V2','V3','V4')

>>>>

if (!is_tinytex()){install_tinytex()}

@@

#make eegdata dataframes
eegdata <- as.data.frame(eegdata)
eegdata_exp <- as.data.frame(eegdata_exp)
